More than one Author with different Affiliations

### 2012-04-23 paper/ms.tex
Added MCMC implementation section

\section{Proposal Distributions}

\begin{thebibliography}{99}
\bibitem[Kelly et al.(2008)]{2008ApJ...682..874K} Kelly, B.~C., Fan, X., 
\& Vestergaard, M.\ 2008, ApJ, 682, 874 
\end{thebibliography}

>>>>

\section{MCMC Implementation}
\subsection{Current}
I am using Diffusive Nested Sampling \citep{dnest}, which is really just
Metropolis-Hastings but targeting a fancy distribution instead of the actual
posterior, and then assigning importance weights when you want the posterior.
Nested Sampling is good because it is invariant under monotonic transformations
of the likelihood function. i.e. the exploration only depends on things like
whether one point is better than another, and not on how much better it is.

\subsection{Future Possibilities}
{\bf Hogg}: {\it I think this problem is important enough and general enough
that we should spend some time working on some ideas there.  If we can sample
over image explanations, our powers in astronomy will be awesome
beyond our wildest imaginings.}

\begin{thebibliography}{99}
\bibitem[\protect\citeauthoryear{Brewer, P{\'a}rtay, 
\& Cs{\'a}nyi}{2011b}]{dnest} Brewer B.~J., P{\'a}rtay L.~B.,
Cs{\'a}nyi G., 2011, Statistics and Computing, 21, 4, 649-656. arXiv:0912.2380

\bibitem[Kelly et al.(2008)]{2008ApJ...682..874K} Kelly, B.~C., Fan, X., 
\& Vestergaard, M.\ 2008, ApJ, 682, 874 
\end{thebibliography}
